---
title: r2dht11 - R to DHT11
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Control your Raspberry Pi's DHT11 sensor from R.

**Acknowledgments:** This package imports the [DHT11](https://github.com/szazo/DHT11_Python) Python library.

## Installation

`r2dht11` is currently only available as a GitHub package.

To install it run the following from an R console:

```{r, eval = FALSE}
if (!require("remotes")) {
  install.packages("remotes")
}
remotes::install_github("jcrodriguez1989/r2dht11", dependencies = TRUE)
```

## Prerequisites

### DHT11 Connection

Please make sure that your DHT11 is correctly connected to your Raspberry Pi. Take note to which GPIO pin is your DHT11 connected.

## Usage

In this example, the DHT11 is connected to the GPIO14 pin:

```{r eval = FALSE}
# Load the library.
library("r2dht11")
# Get a DHT11 sensor instance, which is connected to the GPIO 14 pin.
dht11 <- get_dht11_sensor(14)
# Read the sensor's values.
read_sensor(dht11)
```
